Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes

### 2012-02-22 presentations/ob1_wg_paper/response.tex

\documentclass{article}
\newcommand{\I}{\item}
\newcommand{\Q}[1]{\begin{quote} #1 \end{quote}}
\begin{document}
\section*{Response to Reviewer 1}
We appreciate the reviewer's detailed analysis and critique of the submitted
    publication.
A short response to the reviewer's remarks follows.
\begin{itemize}
\item Reviewer comments: 
    \Q{The method use only waveguides with the same direction of propagation and it is not
    possible to use this method for 2 tilt beams as in the case occurring in the grating
    coupler. first reference of the paper is not really appropriate.}

    The purpose of the first paper is appropriate because it is an example of
    solving the mode conversion for nanophotonics

\item Reviewer comments: 
    \Q{The method uses a 2.5 D approximation that it is not able to calculate accurately the
diffraction losses in the 3rd direction. In the paper, there are no validations of the
design by an accurate 3D method of modeling like FDTD for example.}

    The paper actually does not use a 2.5D approximation. 
    All simulations are in 2D. 
    3D devices will be investigated in a future publication.

\item Reviewer comments:
    \Q{The problem of realization of such coupler is not address. The size of the grid points
use for the modeling is closed to 10 nm and Iam not sure that it is compatible with the
resolution of standard or best lithographic tools. The authors must be added some
comments and if it possible to adapt her design with some rules that consider the
limitations induce by the fabrication.}

    According to the captions of Figs. 2 and following, the highest resolution 
    structures that are even possible are $\lambda_0/42$, where $\lambda_0$
    is the vacuum wavelength of light. 
    Therefore, for the case of $\lambda_0 = 1550 nm$ a \emph{single} pixel is 
    still 37nm $\times$ 37nm in size, from which we infer that the
    characteristic features of all the devices presented are well within
    the resolution of the current lithographic tools.

\item Reviewer comments:
    \Q{The problem of the wavelength tolerance and the alignment tolerances is not address.}

    The goal of this publication is simply to present the objective-first
    algorithm. 
    Robustness considerations are left to subsequent investigations.

\item Reviewer comments:
    \Q{In this paper, there are no comparison with other solution of coupling structure
describe in the literature. So, it is difficult to evaluate if this new method can be bring
realistic solutions of waveguide couplers.}

    The reviewer's point is valid.
    However, the reason why comparable solutions are not evaluated is largely
    because no competing methods for designing arbitrary mode couplers exist.
\end{itemize}

\section*{Response to Reviewer 2}
We appreciate the reviewer's encouraging remarks and suggestions.

The reviewer suggested that
\Q{ However, the use of the permittivity of a large range makes the example impractical and limit the method to theoretical analysis. I suggest the authors give at least one example (e.g. 1x2 coupler) to show its capability for the binary structure. }

This suggestion is very useful, however, we would like to defer the design of
    completely binary structures to a later publication.
\end{document}

### 2012-02-22 presentations/ob1_wg_paper/paper.tex
Updated paper with response.

\begin{document}
\title{Objective-First Design of 
    High-Efficiency, Small-Footprint Couplers Between 
    Arbitrary Nanophotonic Waveguide Modes}
\author{Jesse Lu and Jelena Vu\v{c}kovi\'{c}}
\address{Stanford University, Stanford, California, USA.}
\email{jesselu@stanford.edu}

@@

\begin{thebibliography}{99}
\bibitem{fibergrating} Y. Tang, Z. Wang, L. Wosinski, U. Westergren, and S. He,
    ``Highly efficient nonuniform grating coupler for silicon-on-insulator 
    nanophotonic circuits,''
    Opt. Lett. \textbf{35}, 1290-1292 (2010)
\bibitem{ridge}  K. K. Lee, D. R. Lim, L.C. Kimerling, J. Shin, and F. Cerrina, 
    ``Fabrication of ultralow-loss Si/SiO2 waveguides by roughness reduction,''
    Opt. Lett. \textbf{26}, 1888-1890 (2001)
\bibitem{pcslow} Y. A. Vlasov, M. O'Boyle, H. F. Hamann, and S. J. McNab,
    ``Active control of slow light on a chip with photonic crystal waveguides,''
    Nature \textbf{438}, 65-69 (2005)
\bibitem{slotfocus} M. Lipson, 
    ``Guiding, Modulating, and Emitting Light on 
    Silicon-Challenges and Opportunities,'' 
    J. Lightwave Technol. \textbf{23}, 4222-4238 (2005) 
\bibitem{active} J. Van Campenhout, P. Rojo Romeo, P. Regreny, C. Seassal, 
    D. Van Thourhout, S. Verstuyft, L. Di Cioccio, J.-M. Fedeli, 
    C. Lagahe, and R. Baets, 
    ``Electrically pumped InP-based microdisk lasers integrated with a 
    nanophotonic silicon-on-insulator waveguide circuit,'' 
    Opt. Express \textbf{15}, 6744-6749 (20.75) 
\bibitem{metallic} L. Tang, S. E. Kocabas, S. Latif, A. K. Okyay, 
    D. S. Ly-Gagnon, K. C. Saraswat and D. A. B. Miller, 
    ``Nanometre-Scale Germanium Photodetector Enhanced by a 
    Near-Infrared Dipole Antenna,'' 
    Nature Photonics \textbf{2}, 226 – 229 (2008) 
% \bibitem{fwadia} V. R. Almeida, R. R. Panepucci, and M. Lipson, 
%     ``Nanotaper for compact mode conversion,'' 
%     Opt. Lett. \textbf{28}, 1302-1304 (2003) 
% \bibitem{wwadia} S. G. Johnson, P. Bienstman,  M. A. Skorobogatiy, 
%     M. Ibanescu1, E. Lidorikis, and J. D. Joannopoulos,
%     ``Adiabatic theorem and continuous coupled-mode theory for 
%     efficient taper transitions in photonic crystals,''
%     Phys. Rev. E \textbf{66}, 066608 (2002)
% \bibitem{deriv} F. Wang, J. S. Jensen, O. Sigmund, 
%     ``Robust topology optimization of photonic crystal waveguides with 
%     tailored dispersion properties.'' 
%     J. Opt. Soc. Am. B \textbf{28}, 387-397 (2011)
% \bibitem{boydbook} S. Boyd, and L. Vandenberghe, 
%     \emph{Convex Optimization} 
%     (Cambridge University Press, 2004)
\bibitem{prevwork} J. Lu, S. Boyd, and J. Vuckovic, 
    ``Inverse design of a three-dimensional nanophotonic resonator,''
    Opt. Express \textbf{19}, 10563-10.750 (2011) 
\bibitem{code} \url{www.github.com/JesseLu/objective-first}
\end{thebibliography}

@@

The motivation behind this formulation is two-fold.
First, this approach allows is to arrive at a locally-optimal design rapidly 
    by allowing $x$ and $p$ to vary independently, 
    as opposed to Eq.~\ref{eq:adj}
    where the value of $x$ is completely dependent on $p$.
Second, it enables an increase in the likelihood of 
    arriving at a high efficiency design
    by forcibly imposing $f(x) = 0$,
    and thereby circumvents any local optima consisting of
    low-performance devices.

@@

In order to produce a method applicable 
    to the design of any linear nanophotonic device,
    we note that its performance
    will be completely characterized by the fields along its boundary,
    and therefore, 
    we choose a boundary-value formulation for the design objective.
Namely, we first compute the boundary fields needed to obtain
    perfect performance, $H_z^\text{perfect}$,
    and then form the design objective as
    \begin{equation}
    f(x) = f(H_z) = \begin{bmatrix}
        H_z - H_z^\text{perfect} \\
        \frac{\partial H_z}{\partial n} - 
            \frac{\partial H_z^\text{perfect}}{\partial n}
        \end{bmatrix}_\text{boundary}
        = 0,
    \end{equation}
    where $\partial H_z / \partial n$ 
    denotes the spatial derivative in the direction normal to the boundary.

>>>>

\begin{document}
\title{Objective-first design of 
    high-efficiency, small-footprint couplers between 
    arbitrary nanophotonic waveguide modes}
\author{Jesse Lu$^\ast$ and Jelena Vu\v{c}kovi\'{c}}
\address{Stanford University, Stanford, California, USA.}
\email{\url{jesselu@stanford.edu}}

@@

\begin{thebibliography}{99}
\bibitem{fibergrating} Y. Tang, Z. Wang, L. Wosinski, U. Westergren, and S. He,
    ``Highly efficient nonuniform grating coupler for silicon-on-insulator 
    nanophotonic circuits,''
    Opt. Lett. \textbf{35}, 1290-1292 (2010).
\bibitem{ridge}  K. K. Lee, D. R. Lim, L.C. Kimerling, J. Shin, and F. Cerrina, 
    ``Fabrication of ultralow-loss Si/SiO2 waveguides by roughness reduction,''
    Opt. Lett. \textbf{26}, 1888-1890 (2001).
\bibitem{pcslow} Y. A. Vlasov, M. O'Boyle, H. F. Hamann, and S. J. McNab,
    ``Active control of slow light on a chip with photonic crystal waveguides,''
    Nature \textbf{438}, 65-69 (2005).
\bibitem{slotfocus} M. Lipson, 
    ``Guiding, modulating, and emitting light on 
    silicon-challenges and opportunities,'' 
    J. Lightwave Technol. \textbf{23}, 4222-4238 (2005).
\bibitem{active} J. Van Campenhout, P. Rojo Romeo, P. Regreny, C. Seassal, 
    D. Van Thourhout, S. Verstuyft, L. Di Cioccio, J.-M. Fedeli, 
    C. Lagahe, and R. Baets, 
    ``Electrically pumped InP-based microdisk lasers integrated with a 
    nanophotonic silicon-on-insulator waveguide circuit,'' 
    Opt. Express \textbf{15}, 6744-6749 (2007).
\bibitem{metallic} L. Tang, S. E. Kocabas, S. Latif, A. K. Okyay, 
    D. S. Ly-Gagnon, K. C. Saraswat, and D. A. B. Miller, 
    ``Nanometre-scale germanium photodetector enhanced by a 
    near-infrared dipole antenna,'' 
    Nature Photonics \textbf{2}, 226 – 229 (2008).
% \bibitem{fwadia} V. R. Almeida, R. R. Panepucci, and M. Lipson, 
%     ``Nanotaper for compact mode conversion,'' 
%     Opt. Lett. \textbf{28}, 1302-1304 (2003) 
% \bibitem{wwadia} S. G. Johnson, P. Bienstman,  M. A. Skorobogatiy, 
%     M. Ibanescu1, E. Lidorikis, and J. D. Joannopoulos,
%     ``Adiabatic theorem and continuous coupled-mode theory for 
%     efficient taper transitions in photonic crystals,''
%     Phys. Rev. E \textbf{66}, 066608 (2002)
% \bibitem{deriv} F. Wang, J. S. Jensen, O. Sigmund, 
%     ``Robust topology optimization of photonic crystal waveguides with 
%     tailored dispersion properties.'' 
%     J. Opt. Soc. Am. B \textbf{28}, 387-397 (2011)
% \bibitem{boydbook} S. Boyd, and L. Vandenberghe, 
%     \emph{Convex Optimization} 
%     (Cambridge University Press, 2004)
\bibitem{prevwork} J. Lu, S. Boyd, and J. Vuckovic, 
    ``Inverse design of a three-dimensional nanophotonic resonator,''
    Opt. Express \textbf{19}, 10563-10.750 (2011). 
\bibitem{code} \url{www.github.com/JesseLu/objective-first}
\end{thebibliography}

@@

The motivation behind this formulation is two-fold.
First, this approach allows one to arrive at a locally-optimal design rapidly 
    by allowing $x$ and $p$ to vary independently, 
    as opposed to Eq.~\ref{eq:adj}
    where the value of $x$ is completely dependent on $p$.
Second, it enables an increase in the likelihood of 
    arriving at a high efficiency design
    by forcibly imposing $f(x) = 0$,
    and thereby circumvents any local optima consisting of
    low-performance devices.

@@

In order to produce a method applicable 
    to the design of any linear nanophotonic device,
    we note that its performance
    will be completely characterized by the fields along its boundary,
    and therefore, 
    we choose a boundary-value formulation for the design objective 
    as shown in Fig.~\ref{fig:intro}.
Namely, we first compute the boundary fields needed to obtain
    perfect performance, $H_z^\text{perfect}$,
    and then form the design objective as
    \begin{equation}
    f(x) = f(H_z) = \begin{bmatrix}
        H_z - H_z^\text{perfect} \\
        \frac{\partial H_z}{\partial n} - 
            \frac{\partial H_z^\text{perfect}}{\partial n}
        \end{bmatrix}_\text{boundary}
        = 0,
    \end{equation}
    where $\partial H_z / \partial n$ 
    denotes the spatial derivative in the direction normal to the boundary.
